---
title: | 
  New Models
author: 
  name: 

lang: en
date: today
date-format: "D MMMM YYYY"
editor: source
execute:
  echo: false
  warning: false
  message: false
  include: false

toc: true
toc-depth: 3
number-sections: false
format:
  pdf:
    documentclass: article
    latex-engine: xelatex
    colorlinks: false
    mainfont: "CMU Serif"
    fontsize: 11pt
    papersize: a4
    geometry: 
      - top=3cm
      - bottom=3cm
      - left=2.5cm
      - right=2.5cm

header-includes:
    - \usepackage{pdflscape}
    - \newcommand{\blandscape}{\begin{landscape}}
    - \newcommand{\elandscape}{\end{landscape}}

---
```{r}
#| label: load and install pkgs
packages <- c("tidyverse", "texreg", "marginaleffects", "ggpubr", "MASS", "DescTools", "conflicted")

load_p <- function(){
  for (p in packages) {
    if (!requireNamespace(p, quietly = TRUE)) {
      install.packages(p)
    }
    library(p, character.only = TRUE)
  }
}

load_p()

## conflicts
conflict_scout()
conflicts_prefer(dplyr::select)
conflicts_prefer(dplyr::filter)
```

```{r}
#| label: reading data
data <- readr::read_csv("data/data.csv")
```

```{r}
#| label: self-eff index
data <- data |> 
    rowwise() |> 
    mutate(
      self_eff = mean(c_across(SE01_01:SE01_04), na.rm = TRUE),
      pri_con = mean(c_across(c(PC01_01, PC01_02, PC01_04:PC01_07)), na.rm = TRUE),
      grats_gen = mean(c_across(GR02_01:GR02_05), na.rm = TRUE),
      pri_delib = mean(c_across(PD01_01:PD01_05), na.rm = TRUE),
      trust_community = mean(c_across(TR01_01:TR01_03), na.rm = TRUE),
      trust_provider = mean(c_across(TR01_04:TR01_06), na.rm = TRUE),
      trust_system = mean(c_across(TR01_07:TR01_09), na.rm = TRUE),
      trust_spec = mean(c_across(trust_community:trust_system), na.rm = TRUE)
      ) |> 
    ungroup()


data <- data |> 
  mutate(communicated = if_else(words > 0, 1, 0))
```

\clearpage
# Engagement in Communication (Logistic Regression Models)

```{r}
#| label: lr models communicated

commented_lr_1 <- glm(communicated ~ 
    self_eff + version,
    data = data,
    family = binomial(link = "logit")
    )

commented_lr_2 <- glm(communicated ~ 
    pri_con + version,
    data = data,
    family = binomial(link = "logit")
    )

commented_lr_3 <- glm(communicated ~ 
    grats_gen + version,
    data = data,
    family = binomial(link = "logit")
    )

commented_lr_4 <- glm(communicated ~ 
    pri_delib + version,
    data = data,
    family = binomial(link = "logit")
    )

commented_lr_5 <- glm(communicated ~ 
    trust_spec + version,
    data = data,
    family = binomial(link = "logit")
    )
```


\blandscape
```{r}
#| label: tbl-comm-lr
#| tbl-cap: "Effect of Privacy Calculus Variables on Decision to Communicate"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(commented_lr_1,
       commented_lr_2,
       commented_lr_3,
       commented_lr_4,
       commented_lr_5
       ),
  custom.model.names = c(
    "LR Model 1",
    "LR Model 2",
    "LR Model 3",
    "LR Model 4",
    "LR Model 5"
    ),
  custom.header = list(
  "DV: Communicated" = 1:5
  ),
  custom.coef.map = list(
    "self_eff" = "Self-Efficacy",
    "pri_con" = "Privacy Concerns",
    "grats_gen" = "Gratifications",
    "pri_delib" = "Privacy Deliberations",
    "trust_spec" = "Trust",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    #"male" = "Male",
    # "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("Logit", "Logit", "Logit", "Logit", "Logit")
    #"Education Controls" = c("No", "No", "No", "No", "No")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

# Amount of Communication (OLS/NegBin Regression Models)

\clearpage
## Self-Efficacy

```{r}
#| label: self-eff models (dv words)

words_log_ols1_se <- glm(words_log ~ 
    self_eff + version,
    data = data,
    family = "gaussian"
    )

words_log_ols2_se <- glm(words_log ~ 
    self_eff * version,
    data = data,
    family = "gaussian"
    )

words_log_ols3_se <- glm(words_log ~ 
    self_eff * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

words_nb1_se <- glm.nb(words ~ 
    self_eff + version,
    data = data
    )

words_nb2_se <- glm.nb(words ~ 
    self_eff * version,
    data = data
    )

words_nb3_se <- glm.nb(words ~ 
    self_eff * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )
```


\blandscape
```{r}
#| label: tbl-selfeffmodels
#| tbl-cap: "Effect of Self-Efficacy on Communication Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(words_log_ols1_se,
       words_log_ols2_se,
       words_log_ols3_se,
       words_nb1_se,
       words_nb2_se,
       words_nb3_se
       ),
  custom.model.names = c(
    "Model 1",
    "Model 2",
    "Model 3",
    "Model 4",
    "Model 5",
    "Model 6"
    ),
  custom.header = list(
  "DV: Words Log" = 1:3, "DV: Words" = 4:6
  ),
  custom.coef.map = list(
    "self_eff" = "Self-Efficacy",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "self_eff:versionLike" = "Self-Efficacy x Like",
    "self_eff:versionLike & dislike" = "Self-Efficacy x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

```{r}
#| label: models self-disclosure self_eff

sd_log_ols1_se <- glm(self_dis_log ~ 
    self_eff + version,
    data = data,
    family = "gaussian"
    )

sd_log_ols2_se <- glm(self_dis_log ~ 
    self_eff * version,
    data = data,
    family = "gaussian"
    )

sd_log_ols3_se <- glm(self_dis_log ~ 
    self_eff * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

sd_nb1_se <- glm.nb(self_dis ~ 
    self_eff + version,
    data = data
    )

sd_nb2_se <- glm.nb(self_dis ~ 
    self_eff * version,
    data = data
    )

sd_nb3_se <- glm.nb(self_dis ~ 
    self_eff * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )

```

\blandscape
```{r}
#| label: tbl-selfdisc-models-se
#| tbl-cap: "Effect of Self-Efficacy on Communication (incl. Reactions) Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(sd_log_ols1_se,
       sd_log_ols2_se,
       sd_log_ols3_se,
       sd_nb1_se,
       sd_nb2_se,
       sd_nb3_se
       ),
  custom.model.names = c(
    "Model 7",
    "Model 8",
    "Model 9",
    "Model 10",
    "Model 11",
    "Model 12"
    ),
  custom.header = list(
  "DV: Self-Disclosure Log" = 1:3, "DV: Self-Disclosure" = 4:6
  ),
  custom.coef.map = list(
    "self_eff" = "Self-Efficacy",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "self_eff:versionLike" = "Self-Efficacy x Like",
    "self_eff:versionLike & dislike" = "Self-Efficacy x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

```{r}
#| label: fig-meplot
#| include: true
#| fig-cap: "Marginal Effects of Self-Efficacy on Communication"
#| fig-cap-location: bottom

me_theme <- theme_bw(base_size = 14) +
  theme(
    panel.grid.major = element_line(
      linetype = "dashed",
      color = "gray80",
      linewidth = .2
    ),
    panel.grid.minor = element_blank(),
    axis.text.x  = element_text(size = 8),
    axis.text.y  = element_text(size = 8),
    axis.title.x = element_text(size = 10, margin = margin(t = 15)),
    axis.title.y = element_text(size = 10, margin = margin(r = 15)),
    legend.title = element_text(size = 10),
    legend.position = "bottom"
  )

# Model A: marginal effect of self-eff conditional on affordance, dv words log
marg_A <- plot_slopes(
  words_log_ols3_se,
  variables = "self_eff",
  condition = "version",
  conf_level = 0.95,
) +
  geom_rug(
    data = data,
    mapping = aes(x = version),
    sides = "b",
    inherit.aes = FALSE,
    colour = "black",
    alpha = 0.6,
    size = 0.3,
    length = grid::unit(0.03, "npc")
  ) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  me_theme +
  labs(
    x = "Affordance",
    y = "Marginal Effect of Self-Efficacy",
    caption = "Model 3"
  )

# Model B: marginal effect of self-eff conditional on affordance, dv self-disclosure log
marg_B <- plot_slopes(
  sd_log_ols3_se,
  variables = "self_eff",
  condition = "version",
  conf_level = 0.95
) +
  geom_rug(
    data = data,
    mapping = aes(x = version),
    sides = "b",
    inherit.aes = FALSE,
    colour = "black",
    alpha = 0.6,
    size = 0.3,
    length = grid::unit(0.03, "npc")
  ) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  me_theme +
  labs(
    x = "Affordance",
    y = "Marginal Effect of Self-Efficacy",
    caption = "Model 9"
  )


marg_all <- ggarrange(
  marg_A, marg_B,
  ncol = 2, nrow = 1,
  common.legend = TRUE,
  legend = "bottom"
)

marg_all
```

```{r}
#| label: fig-predplot
#| include: true
#| fig-cap: "Predicted Probabilities for Words Log (Model 3)"
#| fig-cap-location: bottom

data_pred <- model.frame(words_log_ols3_se)

new_vals <- expand.grid(
  self_eff = seq(1, 7, by = 0.25),
  version = c("Control", "Like", "Like & dislike"),
  male = Mode(data$male, na.rm = T),
  age = mean(data$age, na.rm = T),
  edu_fac = Mode(data$edu_fac, na.rm = T)
)

pred <- new_vals |> 
  mutate(yhat = predict(words_log_ols3_se, new_vals))

pred |> 
  filter(version != "Like & dislike") |> 
  ggplot(aes(x = self_eff, y = yhat, color = version)) +
  geom_line() +
  theme_bw() +
  theme(
    legend.position = "bottom",
  ) +
  labs(x = "Self-Efficacy", y = "Predicted Words Log",
    color = "Affordance")
```

\clearpage
## Privacy Concerns

```{r}
#| label: pri-con models (dv words)

words_log_ols1_pc <- glm(words_log ~ 
    pri_con + version,
    data = data,
    family = "gaussian"
    )

words_log_ols2_pc <- glm(words_log ~ 
    pri_con * version,
    data = data,
    family = "gaussian"
    )

words_log_ols3_pc <- glm(words_log ~ 
    pri_con * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

words_nb1_pc <- glm.nb(words ~ 
    pri_con + version,
    data = data
    )

words_nb2_pc <- glm.nb(words ~ 
    pri_con * version,
    data = data
    )

words_nb3_pc <- glm.nb(words ~ 
    pri_con * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )
```

\blandscape
```{r}
#| label: tbl-privconmodels
#| tbl-cap: "Effect of Privacy Concerns on Communication Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(words_log_ols1_pc,
       words_log_ols2_pc,
       words_log_ols3_pc,
       words_nb1_pc,
       words_nb2_pc,
       words_nb3_pc
       ),
  custom.model.names = c(
    "Model 13",
    "Model 14",
    "Model 15",
    "Model 16",
    "Model 17",
    "Model 18"
    ),
  custom.header = list(
  "DV: Words Log" = 1:3, "DV: Words" = 4:6
  ),
  custom.coef.map = list(
    "pri_con" = "Privacy Concerns",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "pri_con:versionLike" = "Privacy Concerns x Like",
    "pri_con:versionLike & dislike" = "Privacy Concerns x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

```{r}
#| label: models self-disclosure pri_con

sd_log_ols1_pc <- glm(self_dis_log ~ 
    pri_con + version,
    data = data,
    family = "gaussian"
    )

sd_log_ols2_pc <- glm(self_dis_log ~ 
    pri_con * version,
    data = data,
    family = "gaussian"
    )

sd_log_ols3_pc <- glm(self_dis_log ~ 
    pri_con * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

sd_nb1_pc <- glm.nb(self_dis ~ 
    pri_con + version,
    data = data
    )

sd_nb2_pc <- glm.nb(self_dis ~ 
    pri_con * version,
    data = data
    )

sd_nb3_pc <- glm.nb(self_dis ~ 
    pri_con * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )

```

\blandscape
```{r}
#| label: tbl-selfdisc-models-pc
#| tbl-cap: "Effect of Privacy Concerns on Communication (incl. Reactions) Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(sd_log_ols1_pc,
       sd_log_ols2_pc,
       sd_log_ols3_pc,
       sd_nb1_pc,
       sd_nb2_pc,
       sd_nb3_pc
       ),
  custom.model.names = c(
    "Model 19",
    "Model 20",
    "Model 21",
    "Model 22",
    "Model 23",
    "Model 24"
    ),
  custom.header = list(
  "DV: Self-Disclosure Log" = 1:3, "DV: Self-Disclosure" = 4:6
  ),
  custom.coef.map = list(
    "pri_con" = "Privacy Concerns",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "pri_con:versionLike" = "Privacy Concerns x Like",
    "pri_con:versionLike & dislike" = "Privacy Concerns x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

\clearpage
## Gratifications

```{r}
#| label: grats-gen models (dv words)

words_log_ols1_gg <- glm(words_log ~ 
    grats_gen + version,
    data = data,
    family = "gaussian"
    )

words_log_ols2_gg <- glm(words_log ~ 
    grats_gen * version,
    data = data,
    family = "gaussian"
    )

words_log_ols3_gg <- glm(words_log ~ 
    grats_gen * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

words_nb1_gg <- glm.nb(words ~ 
    grats_gen + version,
    data = data
    )

words_nb2_gg <- glm.nb(words ~ 
    grats_gen * version,
    data = data
    )

words_nb3_gg <- glm.nb(words ~ 
    grats_gen * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )
```

\blandscape
```{r}
#| label: tbl-gratsgenmodels
#| tbl-cap: "Effect of Gratifications on Communication Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(words_log_ols1_gg,
       words_log_ols2_gg,
       words_log_ols3_gg,
       words_nb1_gg,
       words_nb2_gg,
       words_nb3_gg
       ),
  custom.model.names = c(
    "Model 25",
    "Model 26",
    "Model 27",
    "Model 28",
    "Model 29",
    "Model 30"
    ),
  custom.header = list(
  "DV: Words Log" = 1:3, "DV: Words" = 4:6
  ),
  custom.coef.map = list(
    "grats_gen" = "Gratifications",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "grats_gen:versionLike" = "Gratifications x Like",
    "grats_gen:versionLike & dislike" = "Gratifications x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

```{r}
#| label: models self-disclosure grats_gen

sd_log_ols1_gg <- glm(self_dis_log ~ 
    grats_gen + version,
    data = data,
    family = "gaussian"
    )

sd_log_ols2_gg <- glm(self_dis_log ~ 
    grats_gen * version,
    data = data,
    family = "gaussian"
    )

sd_log_ols3_gg <- glm(self_dis_log ~ 
    grats_gen * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

sd_nb1_gg <- glm.nb(self_dis ~ 
    grats_gen + version,
    data = data
    )

sd_nb2_gg <- glm.nb(self_dis ~ 
    grats_gen * version,
    data = data
    )

sd_nb3_gg <- glm.nb(self_dis ~ 
    grats_gen * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )

```

\blandscape
```{r}
#| label: tbl-selfdisc-models-gg
#| tbl-cap: "Effect of Gratifications on Communication (incl. Reactions) Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(sd_log_ols1_gg,
       sd_log_ols2_gg,
       sd_log_ols3_gg,
       sd_nb1_gg,
       sd_nb2_gg,
       sd_nb3_gg
       ),
  custom.model.names = c(
    "Model 31",
    "Model 32",
    "Model 33",
    "Model 34",
    "Model 35",
    "Model 36"
    ),
  custom.header = list(
  "DV: Self-Disclosure Log" = 1:3, "DV: Self-Disclosure" = 4:6
  ),
  custom.coef.map = list(
    "grats_gen" = "Gratifications",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "grats_gen:versionLike" = "Gratifications x Like",
    "grats_gen:versionLike & dislike" = "Gratifications x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

\clearpage
## Privacy Deliberations

```{r}
#| label: pri_delib models (dv words)

words_log_ols1_pd <- glm(words_log ~ 
    pri_delib + version,
    data = data,
    family = "gaussian"
    )

words_log_ols2_pd <- glm(words_log ~ 
    pri_delib * version,
    data = data,
    family = "gaussian"
    )

words_log_ols3_pd <- glm(words_log ~ 
    pri_delib * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

words_nb1_pd <- glm.nb(words ~ 
    pri_delib + version,
    data = data
    )

words_nb2_pd <- glm.nb(words ~ 
    pri_delib * version,
    data = data
    )

words_nb3_pd <- glm.nb(words ~ 
    pri_delib * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )
```

\blandscape
```{r}
#| label: tbl-privdelibmodels
#| tbl-cap: "Effect of Privacy Deliberations on Communication Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(words_log_ols1_pd,
       words_log_ols2_pd,
       words_log_ols3_pd,
       words_nb1_pd,
       words_nb2_pd,
       words_nb3_pd
       ),
  custom.model.names = c(
    "Model 37",
    "Model 38",
    "Model 39",
    "Model 40",
    "Model 41",
    "Model 42"
    ),
  custom.header = list(
  "DV: Words Log" = 1:3, "DV: Words" = 4:6
  ),
  custom.coef.map = list(
    "pri_delib" = "Privacy Deliberations",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "pri_delib:versionLike" = "Privacy Deliberations x Like",
    "pri_delib:versionLike & dislike" = "Privacy Deliberations x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

```{r}
#| label: models self-disclosure pri_delib

sd_log_ols1_pd <- glm(self_dis_log ~ 
    pri_delib + version,
    data = data,
    family = "gaussian"
    )

sd_log_ols2_pd <- glm(self_dis_log ~ 
    pri_delib * version,
    data = data,
    family = "gaussian"
    )

sd_log_ols3_pd <- glm(self_dis_log ~ 
    pri_delib * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

sd_nb1_pd <- glm.nb(self_dis ~ 
    pri_delib + version,
    data = data
    )

sd_nb2_pd <- glm.nb(self_dis ~ 
    pri_delib * version,
    data = data
    )

sd_nb3_pd <- glm.nb(self_dis ~ 
    pri_delib * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )

```

\blandscape
```{r}
#| label: tbl-selfdisc-models-pd
#| tbl-cap: "Effect of Privacy Deliberations on Communication (incl. Reactions) Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(sd_log_ols1_pd,
       sd_log_ols2_pd,
       sd_log_ols3_pd,
       sd_nb1_pd,
       sd_nb2_pd,
       sd_nb3_pd
       ),
  custom.model.names = c(
    "Model 43",
    "Model 44",
    "Model 45",
    "Model 46",
    "Model 47",
    "Model 48"
    ),
  custom.header = list(
  "DV: Self-Disclosure Log" = 1:3, "DV: Self-Disclosure" = 4:6
  ),
  custom.coef.map = list(
    "pri_delib" = "Privacy Deliberations",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "pri_delib:versionLike" = "Privacy Deliberations x Like",
    "pri_delib:versionLike & dislike" = "Privacy Deliberations x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape


\clearpage
## Trust

```{r}
#| label: trust_spec models (dv words)

words_log_ols1_ts <- glm(words_log ~ 
    trust_spec + version,
    data = data,
    family = "gaussian"
    )

words_log_ols2_ts <- glm(words_log ~ 
    trust_spec * version,
    data = data,
    family = "gaussian"
    )

words_log_ols3_ts <- glm(words_log ~ 
    trust_spec * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

words_nb1_ts <- glm.nb(words ~ 
    trust_spec + version,
    data = data
    )

words_nb2_ts <- glm.nb(words ~ 
    trust_spec * version,
    data = data
    )

words_nb3_ts <- glm.nb(words ~ 
    trust_spec * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )
```

\blandscape
```{r}
#| label: tbl-trustspecbmodels
#| tbl-cap: "Effect of Trust on Communication Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(words_log_ols1_ts,
       words_log_ols2_ts,
       words_log_ols3_ts,
       words_nb1_ts,
       words_nb2_ts,
       words_nb3_ts
       ),
  custom.model.names = c(
    "Model 49",
    "Model 50",
    "Model 51",
    "Model 52",
    "Model 53",
    "Model 54"
    ),
  custom.header = list(
  "DV: Words Log" = 1:3, "DV: Words" = 4:6
  ),
  custom.coef.map = list(
    "trust_spec" = "Trust",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "trust_spec:versionLike" = "Trust x Like",
    "trust_spec:versionLike & dislike" = "Trust x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

```{r}
#| label: models self-disclosure trust_spec

sd_log_ols1_ts <- glm(self_dis_log ~ 
    trust_spec + version,
    data = data,
    family = "gaussian"
    )

sd_log_ols2_ts <- glm(self_dis_log ~ 
    trust_spec * version,
    data = data,
    family = "gaussian"
    )

sd_log_ols3_ts <- glm(self_dis_log ~ 
    trust_spec * version + 
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

sd_nb1_ts <- glm.nb(self_dis ~ 
    trust_spec + version,
    data = data
    )

sd_nb2_ts <- glm.nb(self_dis ~ 
    trust_spec * version,
    data = data
    )

sd_nb3_ts <- glm.nb(self_dis ~ 
    trust_spec * version + 
    male + 
    age + 
    edu_fac,
    data = data
    )

```

\blandscape
```{r}
#| label: tbl-selfdisc-models-ts
#| tbl-cap: "Effect of Trust on Communication (incl. Reactions) Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(sd_log_ols1_ts,
       sd_log_ols2_ts,
       sd_log_ols3_ts,
       sd_nb1_ts,
       sd_nb2_ts,
       sd_nb3_ts
       ),
  custom.model.names = c(
    "Model 55",
    "Model 56",
    "Model 57",
    "Model 58",
    "Model 59",
    "Model 60"
    ),
  custom.header = list(
  "DV: Self-Disclosure Log" = 1:3, "DV: Self-Disclosure" = 4:6
  ),
  custom.coef.map = list(
    "trust_spec" = "Trust",
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "trust_spec:versionLike" = "Trust x Like",
    "trust_spec:versionLike & dislike" = "Trust x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

\clearpage
## Full Specifications

```{r}
#| label: models all constructs dv words

words_log_ols1_comp <- glm(words_log ~ 
    self_eff + 
    version +
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec,
    data = data,
    family = "gaussian"
    )

words_log_ols2_comp <- glm(words_log ~ 
    self_eff * version + 
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec,
    data = data,
    family = "gaussian"
    )

words_log_ols3_comp <- glm(words_log ~ 
    self_eff * version + 
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec +
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

words_nb1_comp <- glm.nb(words ~ 
    self_eff + 
    version +
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec,
    data = data
    )

words_nb2_comp <- glm.nb(words ~ 
    self_eff * version + 
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec,
    data = data
    )

words_nb3_comp <- glm.nb(words ~ 
    self_eff * version + 
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec +
    male + 
    age + 
    edu_fac,
    data = data
    )
```


\blandscape
```{r}
#| label: tbl-words-models-complete
#| tbl-cap: "Effect of Privacy Calculus on Communication Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(words_log_ols1_comp,
       words_log_ols2_comp,
       words_log_ols3_comp,
       words_nb1_comp,
       words_nb2_comp,
       words_nb3_comp
       ),
  custom.model.names = c(
    "Model 61",
    "Model 62",
    "Model 63",
    "Model 64",
    "Model 65",
    "Model 66"
    ),
  custom.header = list(
  "DV: Words Log" = 1:3, "DV: Words" = 4:6
  ),
  custom.coef.map = list(
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    self_eff = "Self-Efficacy",
    pri_con =  "Privacy Concerns",
    grats_gen = "Gratifications",
    pri_delib = "Privacy Deliberations",
    "trust_spec" = "Trust",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "self_eff:versionLike" = "Self-Efficacy x Like",
    "self_eff:versionLike & dislike" = "Self-Efficacy x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape


```{r}
#| label: models all constructs dv self-disclosure

sd_log_ols1_comp <- glm(self_dis_log ~ 
    self_eff + 
    version +
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec,
    data = data,
    family = "gaussian"
    )

sd_log_ols2_comp <- glm(self_dis_log ~ 
    self_eff * version + 
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec,
    data = data,
    family = "gaussian"
    )

sd_log_ols3_comp <- glm(self_dis_log ~ 
    self_eff * version + 
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec +
    male + 
    age + 
    edu_fac,
    data = data,
    family = "gaussian"
    )

sd_nb1_comp <- glm.nb(self_dis ~ 
    self_eff + 
    version +
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec,
    data = data
    )

sd_nb2_comp <- glm.nb(self_dis ~ 
    self_eff * version + 
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec,
    data = data
    )

sd_nb3_comp <- glm.nb(self_dis ~ 
    self_eff * version + 
    pri_con + 
    grats_gen + 
    pri_delib +
    trust_spec +
    male + 
    age + 
    edu_fac,
    data = data
    )
```


\blandscape
```{r}
#| label: tbl-selfdisc-models-complete
#| tbl-cap: "Effect of Privacy Calculus on Communication (incl. Reactions) Conditional on Affordandces"
#| tbl-cap-location: bottom
#| results: asis
#| output: true
#| include: true

texreg(
  list(sd_log_ols1_comp,
       sd_log_ols2_comp,
       sd_log_ols3_comp,
       sd_nb1_comp,
       sd_nb2_comp,
       sd_nb3_comp
       ),
  custom.model.names = c(
    "Model 67",
    "Model 68",
    "Model 69",
    "Model 70",
    "Model 71",
    "Model 72"
    ),
  custom.header = list(
  "DV: Self-Disclosure Log" = 1:3, "DV: Self-Disclosure" = 4:6
  ),
  custom.coef.map = list(
    "versionLike" = "Like Button",
    "versionLike & dislike" = "Like Dislike Buttons",
    self_eff = "Self-Efficacy",
    pri_con =  "Privacy Concerns",
    grats_gen = "Gratifications",
    pri_delib = "Privacy Deliberations",
    "trust_spec" = "Trust",
    "male" = "Male",
    "age" = "Age",
    # "edu_facHochschulabschluss" = "Hochschule",
    # "edu_facAbschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = "PolyOberschule",
    # "edu_facFachhochschulreife (Abschluss einer Fachoberschule)" = "Fachoberschule",
    # "edu_facHauptschulabschluss/Volksschulabschluss" = "Hauptschule",
    # "edu_facRealschulabschluss (Mittlere Reife)" = "Realschule",
    # "edu_facNoch Schüler" = "Schüler",
    # "edu_facAnderer Schulabschluss:" = "Schule andere",
    "self_eff:versionLike" = "Self-Efficacy x Like",
    "self_eff:versionLike & dislike" = "Self-Efficacy x Like Dislike",
    "(Intercept)" = "Constant"
  ),
  custom.gof.rows = list(
    "Estimator" = c("OLS", "OLS", "OLS", "NegBin", "NegBin", "NegBin"),
    "Education Controls" = c("No", "No", "Yes", "No", "No", "Yes")
    ),
  digits = 2,
  single.row = FALSE,
  caption.above = TRUE,
  table = FALSE
)
```
\elandscape

# Quality of Self-Disclosure (Multinomial Logistic Regression (MNL) Models)